Countering language attrition with PanLex and the Web of Data

### 2014-02-19 panlex-rdf-paper/2012/MLOD_PanLex/paper_v4.tex
changed texttt to emph and tried to compact table 3

\section{Introduction}
\label{sec:intro}
At present, there are about 7,000 living languages in the world\footnote{\url{http://www-01.sil.org/iso639-3/iso-639-3.tab}}.
%\footnote{\url{http://www-01.sil.org/iso639-3/iso-639-3.tab}. As of 25 January 2014, this list contained 6,975 living individual languages.}
%Nonetheless, processes such as urbanization, nation-state consolidation, and globalization appear to be producing language attrition, with, %for example, the extinction or near-extinction in the last 60 years of from 10\% to over 75\% (depending on the world's region) of all living languages\cite{lang_crisis}.
Nonetheless, processes such as urbanization, nation-state consolidation, and globalization appear to be producing language attrition: For example, in the last 60 years and depending on the world's region, from 10\% to over 75\% of all living languages have become extinct or near-extinct~\cite{lang_crisis}.\todo{Jonathan: Please check statement}
Theorists of biolinguistic diversity argue that the loss of language diversity, the loss of human biological knowledge, and the loss of species diversity are mutually supportive and thus that language preservation and revitalization are essential to the preservation of biological diversity\cite{nettle}.

@@

\subsection{Analysis of the Original Dataset}
\label{sec:analysis}
At the core of the PanLex \emph{project}, there is the PanLex \emph{database}, which is created by editors who consult thousands of lexical sources, such as mono- and multilingual dictionaries, glossaries, standards, and thesauri.
The list of sources that have been and are being consulted is available online\footnote{\url{http://panlex.org/tech/plrefs.shtml}}.
The data based on these sources include single- and multi-word expressions, meanings assigned to them, and related information. Far from being mere copies of the sources, which would not make PanLex data interoperable, the data constitute editors' \emph{interpretations} of various sources' \emph{assertions} that two or more \emph{expressions} share a \emph{meaning}\footnote{\url{http://panlex.org/tech/doc/design/panlex-db-design.pdf}}.
As of January 2014, the database contained about 20 million meanings and 20 million expressions in about 9,200 language varieties based on the consultation of about 1,500 sources by about 20 editors.
The most important entities and relations of PanLex's conceptual model are depicted in \autoref{fig:db-schema} and are explained in more detail below.

@@

%    Users              &         23 \\ % SELECT COUNT(us) FROM us;
\begin{table}
  \centering\begin{scriptsize}
  \begin{tabular}{lrclr}
    Entity             & Instances  & & Entity    & Instances \\
    \cline{1-2}\cline{4-5}
    Denotations        & 54,278,860 & & Languages & 7,843     \\
    Meanings           & 20,773,371 & & Sources   & 4,190     \\
    Expressions        & 19,790,453 & & Users     &    23     \\
    Definitions        &  2,747,892 & & Licenses  &    11     \\
    Language Varieties &      9,310 & & & \\
  \end{tabular}
  \end{scriptsize}
  \caption{Number of instances of main entities in the PanLex database}
  \label{fig:plx-entity-counts}
\end{table}\todo{new license `75 | pl | pup'; What does it mean?}

\subsection{The PanLex vocabulary}
\label{sec:vocabulary}
The entities and relations of the schema described in the previous section serve as the base for the development of the PanLex RDF vocabulary.
In general, all PanLex RDF resources reside in the namespace \texttt{\small <http://ld.panlex.org/plx/>}, abbreviated with \texttt{\small plx}.
An example of the resulting ontology is depicted in \autoref{fig:vocabulary} and summarized as follows.
Unless otherwise noted, the URIs of instances of PanLex classes follow the pattern \emph{plx:\{className\}/\{id\}}, where \{className\} is spelled in lower camel case and the \{id\} is the primary key of the corresponding database table.

\begin{itemize}
  \item Expressions are modeled as instances of the class \texttt{\small plx:Expression}.
    Their original and degraded textual representations become the values of the properties \texttt{\small rdfs:label} and \texttt{\small plx:degradedText}, respectively.
    Their corresponding language variety is stated using \texttt{\small plx:languageVariety}.
  \item For language and language varieties the classes \texttt{\small plx:Language} and \texttt{\small plx:LanguageVariety} are introduced.
    \emph{ISO 639-1} and \emph{ISO 639-3 codes} become instances of the classes \texttt{\small plx:Iso639-1Code} and \texttt{\small plx:Iso639-3Code}.
  \item The RDF analog of the PanLex \emph{meaning} is the \texttt{\small plx:Meaning}.
    Entities of this class may have an identifier assigned with the \texttt{\small plx:identifier} property pointing to an \texttt{\small xsd:string} literal.
    Meanings may also have \emph{definitions}, entities of the \texttt{\small plx:Definition} class, giving a textual representation (\texttt{\small rdfs:label}) in a certain language variety (\texttt{\small plx:languageVariety}).
  \item Following the semantics of the PanLex database, meanings and expressions are linked via \emph{denotations}.
    These are entities of the \texttt{\small plx:Denotation} class pointing to meanings and expressions via the properties \texttt{\small plx:denotationMeaning} and \\ \texttt{\small plx:denotationExpression}.
    Denotations may also have a word class assigned to them.
    This can be achieved with the denotation's \texttt{\small plx:wordClass} property pointing to a \texttt{\small plx:WordClass} entity.
  \item All sources share the \texttt{\small plx:Source} class.
    The characteristics of a source are described using mainly triples with literal objects.
    These are for example \texttt{\small dc:title} to assign the title of a source, \texttt{\small dc:creator} to give an \texttt{\small xsd:string} containing the author's name. At present, we support the different license categories recognized in the database by creating resources of the \texttt{\small plx:License} class.
\end{itemize}

\begin{table}
  \begin{tiny}
  \begin{tabular}{p{52px}p{140px}}
    Class                 & Properties \\
    \toprule
    \texttt{plx:Source} & \mbox{\texttt{plx:registrationDate}, \texttt{rdfs:label}, \texttt{dc:title},}
                            \mbox{\texttt{dc:creator}, \texttt{plx:license}, \texttt{dc:date}, \texttt{plx:quality},}
                            \mbox{\texttt{foaf:homepage}, \texttt{dc:publisher}, \texttt{dbpedia-owl:isbn}} \\
    \midrule
    \texttt{plx:Language} & \texttt{plx:iso639-3Code}, \texttt{plx:iso639-1Code} \\
    \midrule
    \texttt{plx:LanguageVariety}
                          & \texttt{plx:languageVarietyOf}, \texttt{rdfs:label} \\
    \midrule
    \texttt{plx:Iso639-1Code} & \\
    \midrule
    \texttt{plx:Iso639-3Code} & \\
    \midrule
    \texttt{plx:Expression}
                          & \mbox{\texttt{plx:languageVariety}, \texttt{plx:degradedText},} \texttt{rdfs:label} \\
    \midrule
    \texttt{plx:Meaning}
                          & \mbox{\texttt{plx:source}, \texttt{plx:identifier},} \texttt{plx:meaningDefinition} \\
    \midrule
    \texttt{plx:Definition}
                          & \texttt{plx:languageVariety}, \texttt{rdfs:label} \\
    \midrule
    \texttt{plx:Denotation}
                          & \texttt{plx:denotationMeaning}, \texttt{plx:denotationExpression}, \texttt{plx:wordClass} \\
    \midrule
    \texttt{plx:WordClass}  
                          & \texttt{rdfs:label} \\
    \midrule
    \texttt{plx:License}  & \texttt{rdfs:label} \\
    \bottomrule
  \end{tabular}
  \end{tiny}
  \caption{Classes and properties used in the PanLex RDF vocabulary. Note that all \texttt{rdf:type} properties are omitted for brevity.}
  \label{tbl:vocabulary}
\end{table}

@@

\begin{table}
  \centering\begin{scriptsize}
  \begin{tabular}{p{48px}p{62px}p{70px}}
    Panlex                  & lemon                       & GOLD \\
    \midrule
    \texttt{plx:Denotation} & --                          & \texttt{gold:LinguisticSign} \\
    \texttt{plx:Meaning}    & \texttt{lemon:LexicalSense} & \texttt{gold:SemanticUnit} \\
    \texttt{plx:Expression} & \texttt{lemon:LexicalEntry} & \texttt{gold:FormUnit} \\
  \end{tabular}
  \end{scriptsize}
  \caption{Classes considered to be similar across the re-used vocabulary}
  \label{tbl:sameclasses}
\end{table}

\subsection{Vocabulary Reuse}
\label{sec:vocabulary-reuse}
The PanLex vocabulary is based on PanLex's conceptual schema and
enables all of PanLex's data to be directly exposed as RDF.
%Apart from modeling a PanLex RDF vocabulary
Additionally, we also re-use existing vocuabularies, namely
the \emph{Lexicon Model for Ontologies} (lemon)~\cite{lemon2011} as well as the \emph{General Ontology for Linguistic Description} (GOLD)~\cite{farr2003}.
Since these models differ from the PanLex one to some extent, we follow an
incremental approach of aligning the PanLex data with them.
%accordingly. 
% one differ to some
%extend, not the whole schemas were implemented.
\autoref{tbl:sameclasses} shows PanLex classes with their current counterparts
in lemon and GOLD respectively.
The parts implemented in our RDF conversion are displayed in \autoref{fig:goldlemonimplemented}.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/pdf/gold_lemon_implemented.pdf}
  \caption{Parts of the GOLD (left) and lemon model (right) re-used in PanLex (URI prefixes are omitted for brevity)}
  \label{fig:goldlemonimplemented}
\end{figure}

@@

\section{Publishing}
\label{sec:publishing}
With our RDF conversion work, we complement existing
APIs\footnote{\url{http://panlex.org/try/}} with Linked Data, powered by
Pubby\footnote{\tiny{\url{http://wifo5-03.informatik.uni-mannheim.de/pubby/}}},
and two SPARQL
endpoints\footnote{\url{http://ld.panlex.org/vsparql}}
\footnote{\url{http://ld.panlex.org/sparql}}, powered by Sparqlify and Virtuoso,
respectively.
% and \url{http://ld.panlex.org/snorql}}.
An overview is shown in ~\autoref{fig:panlex-architecture}.
The SPARQL browser
\emph{SNORQL}\footnote{\url{https://github.com/kurtjx/SNORQL}} can be accessed
by replacing \emph{sparql} with \emph{snorql} in the respective links. Our SML
views and the interlinking code are hosted on GitHub\footnote{\url{https://github.com/AKSW/PanLex-2-RDF}}.
The created linksets are hosted in the PanLex database and are published together with the other data using the Sparqlify RDB2RDF tool.
Finally, we offer downloads tagged with timestamps of their creation\footnote{\url{http://ld.panlex.org/downloads/releases/}}.
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/pdf/sparqlify_setup02.pdf}
\caption{PanLex architecture}
\label{fig:panlex-architecture}
\end{figure}

@@

\section{Related Work}
\label{sec:related}
PanLex is a project whose editors integrate information discovered from many lexical resources.
The extraction of information from linguistic sources, and techniques for automatically inferring translations,
are relevant work discussed in \cite{panlex_probtrans}.
%A similar approach of linking expressions to meanings is followed by the
% \emph{Global Wordnet Association}.
An important related initiative is the Global Wordnet Association\footnote{\url{http://www.globalwordnet.org/}\vspace{0.7em}},
which offers a platform for sharing wordnets and, among other goals, uniformly representing wordnets
of different languages and establishing a universal index of meaning.
Wordnets are usually focused on the
definition of \emph{synsets} and relations between them in a single language; GWA is helping to transform these single-language synonym silos into a virtual multilingual translation resource. PanLex is approximating that, in a different way, by integrating data from numerous wordnets along with translingual sources into a single graph.
%As already mentioned in PanLex there can be several meaning entities
% representing the same unique sense.
In the Semantic Web context, several standard or quasi-standard vocabularies and ontologies have been developed with the rise of the \emph{Linguistic Linked Open Data} movement.
Examples include the
\emph{Ontologies of Linguistic Annotation} (OLiA)~\cite{olia2010} for modeling
lexicon and machine-readable dictionaries, \emph{POWLA} for modeling linguistic corpora\cite{powla2012} and the \emph{Natural Language Processing Interchange Format} (NIF)\footnote{\url{http://nlp2rdf.org/nif-1-0}}.

>>>>

\section{Introduction}
\label{sec:intro}
At present, there are about 7,000 living languages in the world\footnote{\url{http://www-01.sil.org/iso639-3/iso-639-3.tab}}.
%\footnote{\url{http://www-01.sil.org/iso639-3/iso-639-3.tab}. As of 25 January 2014, this list contained 6,975 living individual languages.}
%Nonetheless, processes such as urbanization, nation-state consolidation, and globalization appear to be producing language attrition, with, %for example, the extinction or near-extinction in the last 60 years of from 10\% to over 75\% (depending on the world's region) of all living languages\cite{lang_crisis}.
Nonetheless, processes such as urbanization, nation-state consolidation, and globalization appear to be producing language attrition: For example, in the last 60 years and depending on the world's region, from 10\% to over 75\% of all living languages have become extinct or near-extinct~\cite{lang_crisis}.
Theorists of biolinguistic diversity argue that the loss of language diversity, the loss of human biological knowledge, and the loss of species diversity are mutually supportive and thus that language preservation and revitalization are essential to the preservation of biological diversity~\cite{nettle}.

@@

\subsection{Analysis of the Original Dataset}
\label{sec:analysis}
At the core of the PanLex \emph{project}, there is the PanLex \emph{database}, which is created by editors who consult thousands of lexical sources, such as mono- and multilingual dictionaries, glossaries, standards, and thesauri.
The list of sources that have been and are being consulted is available online\footnote{\url{http://panlex.org/tech/plrefs.shtml}}.
The data based on these sources include single- and multi-word expressions, meanings assigned to them, and related information. Far from being mere copies of the sources, which would not make PanLex data interoperable, the data constitute editors' \emph{interpretations} of various sources' \emph{assertions} that two or more \emph{expressions} share a \emph{meaning}\footnote{\url{http://panlex.org/tech/doc/design/panlex-db-design.pdf}}.
% PW: I commented the following sentence out since I removed the detailed number of instances table (language varieties identified/with data; source being consulted/already consulted. I used the bigger numbers and in this sentence the smaller numbers are used, which might confuse
%As of January 2014, the database contained about 20 million meanings and 20 million expressions in about 9,200 language varieties based on the consultation of about 1,500 sources by about 20 editors.
The most important entities and relations of PanLex's conceptual model are depicted in \autoref{fig:db-schema} and are explained in more detail below.

@@

%    Users              &         23 \\ % SELECT COUNT(us) FROM us;
\begin{table}
  \centering\begin{scriptsize}
  \begin{tabular}{lrclr}
    Entity             & Instances  & & Entity    & Instances \\
    \cline{1-2}\cline{4-5}
    Denotations        & 54,278,860 & & Languages & 7,843     \\
    Meanings           & 20,773,371 & & Sources   & 4,190     \\
    Expressions        & 19,790,453 & & Users     &    23     \\
    Definitions        &  2,747,892 & & Licenses  &    11     \\
    Language Varieties &      9,310 & & & \\
  \end{tabular}
  \end{scriptsize}
  \caption{Number of instances of main entities in the PanLex database}
  \label{fig:plx-entity-counts}
\end{table}

\subsection{The PanLex vocabulary}
\label{sec:vocabulary}
The entities and relations of the schema described in the previous section serve as the base for the development of the PanLex RDF vocabulary.
In general, all PanLex RDF resources reside in the namespace \emph{<http://ld.panlex.org/plx/>}, abbreviated with \emph{plx}.
An example of the resulting ontology is depicted in \autoref{fig:vocabulary} and summarized as follows.
Unless otherwise noted, the URIs of instances of PanLex classes follow the pattern \emph{plx:\{className\}/\{id\}}, where \{className\} is spelled in lower camel case and the \{id\} is the primary key of the corresponding database table.

\begin{itemize}
  \item Expressions are modeled as instances of the class \emph{plx:Expression}.
    Their original and degraded textual representations become the values of the properties \emph{rdfs:label} and \emph{plx:degradedText}, respectively.
    Their corresponding language variety is stated using \emph{plx:languageVariety}.
  \item For language and language varieties the classes \emph{plx:Language} and \emph{plx:LanguageVariety} are introduced.
    ISO 639-1 and ISO 639-3 codes become instances of the classes \emph{plx:Iso639-1Code} and \emph{plx:Iso639-3Code}.
  \item The RDF analog of the PanLex \emph{meaning} is the \emph{plx:Meaning}.
    Entities of this class may have an identifier assigned with the \emph{plx:identifier} property pointing to an \emph{xsd:string} literal.
    Meanings may also have \emph{definitions}, entities of the \emph{plx:Definition} class, giving a textual representation (\emph{rdfs:label}) in a certain language variety (\emph{plx:languageVariety}).
  \item Following the semantics of the PanLex database, meanings and expressions are linked via \emph{denotations}.
    These are entities of the \emph{plx:Denotation} class pointing to meanings and expressions via the properties \emph{plx:denotationMeaning} and \emph{plx:\-denotation\-Expression}.
    Denotations may also have a word class assigned to them.
    This can be achieved with the denotation's \emph{plx:wordClass} property pointing to a \emph{plx:WordClass} entity.
  \item All sources share the \emph{plx:Source} class.
    The characteristics of a source are described using mainly triples with literal objects.
    These are for example \emph{dc:title} to assign the title of a source, \emph{dc:creator} to give an \emph{xsd:string} containing the author's name.
    At present, we support the different license categories recognized in the database by creating resources of the \emph{plx:License} class.
\end{itemize}

\begin{table}
  \centering
  \begin{scriptsize}
  \fontsize{5.8pt}{5pt}\selectfont
  \begin{tabular}{p{41pt}p{150pt}}
    Class                 & Properties \\
    \toprule
%    \emph{plx:Source} & \emph{plx:registrationDate},\,\emph{rdfs:label},\,\emph{dc:title},\,\emph{dc:creator},\,\emph{dc:quality}, \emph{plx:license},\,\emph{dc:date},\,\emph{foaf:homepage},\,\emph{dc:publisher},\,\emph{dbpedia-owl:isbn} \\
    \emph{plx:Source} & \emph{plx:registrationDate},\,\emph{rdfs:label},\,\emph{dc:title},\,\emph{dc:publisher},\,\emph{dc:quality}, \emph{plx:license},\,\emph{dc:date},\,\emph{foaf:homepage},\,\emph{dc:creator},\,\mbox{\emph{dbpedia-owl:isbn}} \\
    \midrule
    \emph{plx:Language} & \emph{plx:iso639-3Code}, \emph{plx:iso639-1Code} \\
    \midrule
    \emph{plx:LanguageVariety}
                          & \emph{plx:languageVarietyOf}, \emph{rdfs:label} \\
    \midrule
    \mbox{\emph{plx:Iso639-1Code}} & \\
    \midrule
    \mbox{\emph{plx:Iso639-3Code}} & \\
    \midrule
    \emph{plx:Expression}
                          & \emph{plx:languageVariety}, \emph{plx:degradedText}, \emph{rdfs:label} \\
    \midrule
    \emph{plx:Meaning}
                          & \emph{plx:source}, \emph{plx:identifier}, \emph{plx:meaningDefinition} \\
    \midrule
    \emph{plx:Definition}
                          & \emph{plx:languageVariety}, \emph{rdfs:label} \\
    \midrule
    \emph{plx:Denotation}
                          & \emph{plx:denotationMeaning},\,\emph{plx:denotationExpression},\,\emph{plx:wordClass} \\
    \midrule
    \emph{plx:WordClass}  
                          & \emph{rdfs:label} \\
    \midrule
    \emph{plx:License}    & \emph{rdfs:label} \\
    \bottomrule\vspace{3pt}
  \end{tabular}
  \end{scriptsize}
  \caption{Classes and properties used in the PanLex RDF vocabulary. Note that all \emph{rdf:type} properties are omitted for brevity.}
  \label{tbl:vocabulary}
\end{table}

@@

\begin{table}
  \centering\begin{scriptsize}
  \fontsize{6.5pt}{6.4pt}\selectfont
  \begin{tabular}{p{48px}p{62px}p{70px}}
    Panlex                  & lemon                       & GOLD \\
    \midrule
    \emph{plx:Denotation} & --                          & \emph{gold:LinguisticSign} \\
    \emph{plx:Meaning}    & \emph{lemon:LexicalSense} & \emph{gold:SemanticUnit} \\
    \emph{plx:Expression} & \emph{lemon:LexicalEntry} & \emph{gold:FormUnit} \\
  \end{tabular}
  \end{scriptsize}
  \caption{Classes considered to be similar across the re-used vocabulary}
  \label{tbl:sameclasses}
\end{table}

\subsection{Vocabulary Reuse}
\label{sec:vocabulary-reuse}
The PanLex vocabulary is based on PanLex's conceptual schema and
enables all of PanLex's data to be directly exposed as RDF.
%Apart from modeling a PanLex RDF vocabulary
Additionally, we also re-use existing vocabularies, namely
the \emph{Lexicon Model for Ontologies} (lemon)~\cite{lemon2011} as well as the \emph{General Ontology for Linguistic Description} (GOLD)~\cite{farr2003}.
Since these models differ from the PanLex one to some extent, we follow an
incremental approach of aligning the PanLex data with them.
%accordingly. 
% one differ to some
%extend, not the whole schemas were implemented.
\autoref{tbl:sameclasses} shows PanLex classes with their current counterparts
in lemon and GOLD respectively.
The parts implemented in our RDF conversion are displayed in \autoref{fig:goldlemonimplemented}.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/pdf/gold_lemon_implemented.pdf}
  \caption{Parts of the GOLD (left) and lemon model (right) re-used in PanLex (URI prefixes are omitted for brevity)}
  \label{fig:goldlemonimplemented}
\end{figure}

@@

\section{Publishing}
\label{sec:publishing}
With our RDF conversion work, we complement existing
APIs\footnote{\url{http://panlex.org/try/}} with Linked Data, powered by
Pubby\footnote{\tiny{\url{http://wifo5-03.informatik.uni-mannheim.de/pubby/}}},
and two SPARQL
endpoints\footnote{\url{http://ld.panlex.org/vsparql}}
\footnote{\url{http://ld.panlex.org/sparql}}, ran by Sparqlify and Virtuoso,
respectively.
% and \url{http://ld.panlex.org/snorql}}.
An overview is shown in ~\autoref{fig:panlex-architecture}.
The SPARQL browser
\emph{SNORQL}\footnote{\url{https://github.com/kurtjx/SNORQL}} can be accessed
by replacing \emph{sparql} with \emph{snorql} in the respective links. Our SML
views and the interlinking code are hosted on GitHub\footnote{\url{https://github.com/AKSW/PanLex-2-RDF}}.
The created linksets are hosted in the PanLex database and are published together with the other data using the Sparqlify RDB2RDF tool.
Finally, we offer downloads tagged with timestamps of their creation\footnote{\url{http://ld.panlex.org/downloads/releases/}}.
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/pdf/sparqlify_setup02.pdf}
\caption{PanLex architecture}
\label{fig:panlex-architecture}
\end{figure}

@@

\section{Related Work}
\label{sec:related}
PanLex is a project whose editors integrate information discovered from many lexical resources.
The extraction of information from linguistic sources, and techniques for automatically inferring translations,
are relevant work discussed in \cite{panlex_probtrans}.
%A similar approach of linking expressions to meanings is followed by the
% \emph{Global Wordnet Association}.
An important related initiative is the Global Wordnet Association (GWA)\footnote{\url{http://www.globalwordnet.org/}},
which offers a platform for sharing wordnets and, among other goals, uniformly representing wordnets
of different languages and establishing a universal index of meaning.
Wordnets are usually focused on the
definition of \emph{synsets} and relations between them in a single language; GWA is helping to transform these single-language synonym silos into a virtual multilingual translation resource. PanLex is approximating that, in a different way, by integrating data from numerous wordnets along with translingual sources into a single graph.
%As already mentioned in PanLex there can be several meaning entities
% representing the same unique sense.
In the Semantic Web context, several standard or quasi-standard vocabularies and ontologies have been developed with the rise of the \emph{Linguistic Linked Open Data} movement.
Examples include the
\emph{Ontologies of Linguistic Annotation} (OLiA)~\cite{olia2010} for modeling
lexicon and machine-readable dictionaries, \emph{POWLA} for modeling linguistic corpora\cite{powla2012} and the \emph{Natural Language Processing Interchange Format} (NIF)\footnote{\url{http://nlp2rdf.org/nif-1-0}}.
